---
title: "Modeling and prediction for movies with Bayesian Regression Modeling"
author: "Yoshie Toriya"
date: "04/07/2021"
output: html_document
---

## Introduction

I am new as a data scientist at Paramount Pictures and my boss expects me to present what attributes make a movie popular with the data she has acquired. It includes information from Rotten Tomatoes and IMDB for a random sample of movies.

### Load packages and data

Let's load the packages
```{r load-packages, message = FALSE}
library(statsr)
install.packages("rlang")
library(rlang)
library(dplyr)
library(ggplot2)
library(BAS)
library(GGally)
library(grid)
library(tidyr)
```
and data
```{r load-data}
load("movies.Rdata")
```
that consists of 651 observations and 32 variables:
```{r variable details}
str(movies)
```

## Research question

Question for this analysis is, what is the best model to predict audience score and what attributes should it include?<br>
Note as it has been specified to develop a Bayesian regression model to predict `audience_score` from the following explanatory variables: `feature_film`,` drama`, `runtime`, `mpaa_rating_R`, `thtr_rel_year`, `oscar_season`, `summer_season`, `imdb_rating`, `imdb_num_votes`, `critics_score`, `best_pic_nom`, `best_pic_win`, `best_actor_win`, `best_actress_win`, `best_dir_win`, `top200_box`. 

(NOTE) 
Complete Bayesian model selection and report the final model. 

Also perform model diagnostics and interpret coefficients of your final model in context of the data.


* * *

## Part 1: Data collection & Generalizability/Causality

We are provided with the information that “This dataset includes information from Rotten Tomatoes and IMDB for a random sample of movies” regarding the collection of the data.
So based on it being “a random sample”, we could say the results of the analysis could be generalizable. It might also sound otherwise by mentioning Rotten Tomatoes and IMDB, but it does NOT say the data collection was “limited” from their users but merely “included” them, so with no further information I would not deny the generalizability. Causality, however, can be denied as the data collection does not involve random assignment.

* * *

## Part 2: Data manipulation

The following variables are not in the provided dataset, so need to be created:
```{r new_variables} 
movies <- movies %>%
 mutate(feature_film = if_else(title_type == "Feature Film", "yes", "no"))
movies <- movies %>%
 mutate(drama = if_else(genre == "Drama", "yes", "no"))
movies <- movies %>%
 mutate(mpaa_rating_R = if_else(mpaa_rating == "R", "yes", "no") )
movies <- movies %>%
 mutate(oscar_season = if_else((thtr_rel_month >= 10 & thtr_rel_month <= 12), "yes", "no"))
movies <- movies %>%
 mutate(summer_season = if_else((thtr_rel_month >= 5 & thtr_rel_month <= 8), "yes", "no"))
```


* * *

## Part 3: Exploratory data analysis

My EDA begins with deciding the response variable, among “Audience score” on Rotten Tomatoes (RT), “Critics score” also on RT, and “IMDB rating” on IMDB.

First, on the basics; no null value in each of those variables,
```{r check values}
sum(is.na(movies$audience_score)) 
sum(is.na(movies$critics_score)) 
sum(is.na(movies$imdb_rating)) 
sum(is.na(movies$runtime)) 
```

We see there is one observation with na for “runtime”, so I’m removing this one row and will work with new dataset “movies0”.
```{r drop the row with null runtime}
movies0 <- movies %>%
  drop_na(runtime)
```

and the number of movie titles scored per year.
```{r count per year}
mov_count <- movies0 %>%
  select(thtr_rel_year, title) %>%
  group_by(thtr_rel_year) %>%
  summarise(count = n()) 
```

```{r plot count by year}
ggplot(mov_count, aes(x=thtr_rel_year, y=count)) +
  geom_histogram(stat="identity") +
  theme(axis.text.x = element_text(angle = 45)) +
  ggtitle("Count by year") +
  theme(plot.title = element_text(hjust = 0.5)) 
```


```{r reduced dataset}
#dataset with 16 explanatory variables
movies_14var <- movies0 %>%
        select(audience_score, feature_film, drama, runtime, mpaa_rating_R, thtr_rel_year, oscar_season, summer_season, best_pic_nom, best_pic_win, best_actor_win, best_actress_win, best_dir_win, top200_box)
```


Here is the quick summary of the data:
```{r }
summary(movies_14var)
```


```{r bas}
#run regression model
movies_red_bas14 = bas.lm(audience_score ~ ., data = movies_14var, prior = "BIC", modelprior = Bernoulli(1), include.always = ~ ., n.models = 1)

#extract posterior parameters of coefficients
mv_rd.coef14 = coef(movies_red_bas14)
mv_rd.coef14
```

```{r }
par(mar = c(1,1,1,1), mfrow = c(4,4), col.lab = "darkgrey", col.axis = "darkgrey", col = "darkgrey")
plot(mv_rd.coef14, subset = 2:17, ask = F)
```

```{r }
confint(mv_rd.coef14, parm = 2:17)
```

```{r}
#
out14 = confint(mv_rd.coef14)[, 1:2]
#extract the uppper and lower bounds of the credible intervals
names14 = c("posterior mean", "posterior std", colnames(out14))
out14 = cbind(mv_rd.coef14$postmean, mv_rd.coef14$postsd, out14)
colnames(out14) = names14
round(out14, 5)
```


* * *

## Part 4: Modeling

NOTE: Insert code chunks as needed by clicking on the "Insert a new code chunk" 
button above. Make sure that your code is visible in the project you submit. 
Delete this note when before you submit your work.

```{r }
n14 = nrow(movies_14var) # of observations
movies14.lm = lm(audience_score ~ ., data = movies_14var)
# BIC elimination
mv.step = step(movies14.lm, k = log(n14))
```
note: AIC should read as BIC 
```{r }
#using bas.lm to run the model
mv14.BIC = bas.lm(audience_score ~ ., data = movies_14var, prior = "BIC", modelprior = uniform())
mv14.BIC
```

```{r }
#find the index of the model with the largest logmarg
best14 = which.max(mv14.BIC$logmarg)
#retrieve the index of variables n the best model, with 0 as the index of the intercept
bestmodel14 = mv14.BIC$which[[best14]]
bestmodel14
```

```{r }
#create an indicator vector indicating which variables are used in the best model
#first, create a 0 vector with the same dimension of the number of variables in the f
bestgamma14 = rep(0, mv14.BIC$n.vars)
#Change the indicator to 1 when variables are used
bestgamma[bestmodel14 + 1] = 1
bestgamma
```

```{r }
#fit the best BIC model by imposing which variables to be used using the indicators
mv.bestBIC = bas.lm(audience_score ~ ., data = movies_red, prior = "BIC", n.models = 1, bestmodel = bestgamma, modelprior = uniform())

#retrieve coefficients information
mvBIC.coef = coef(mv.bestBIC)

#retrieve bounds of credible intervals
out = confint(mvBIC.coef)[, 1:2]
#combine results and construct summary table
mvBICcoef.BIC = cbind(mvBIC.coef$postmean, mvBIC.coef$postsd, out)
names = c("post mean", "post sd", colnames(out)) 
colnames(mvBICcoef.BIC) = names
mvBICcoef.BIC
```

All credible intervals of the three predictors became narrower meaning smaller posterior standard deviations, and the positive ones shifted to right. It indicates that this is the parsimonious model.

```{r }
mv_bas = bas.lm(audience_score ~ imdb_rating + critics_score + runtime, data = movies_red, prior = "BIC", modelprior = uniform())
round(summary(mv_bas), 3)
print(mv_bas) # obtain marginal posterior inclusion probability
image(mv_bas, rotate = F) #visualization
```

BMA
```{r }
mv_bma.coef = coef(mv_bas)
mv_bma.coef

par(mfrow = c(1,3))
plot(mv_bma.coef, subset = c(2:4))
```
As the plot indicates, with a small mass at 0 and the intervals do not include 0, we can intepret that these predictors are to be included in the model.


* * *

## Part 5: Prediction

Now I want to assess the model by predicting the score, so have picked Snowden among the 2016 movies. imdb_rating is obtained from [IMDB](https://www.imdb.com/title/tt3774114/?ref_=fn_al_tt_1) and critics_rating from 
[Rotten Tomatoes](https://www.rottentomatoes.com/m/snowden).

```{r create a new dataset}
snowden <- data.frame(
  title = c ("Snowden"), 
  title_type = c ("Feature Film"),
  genre = c ("Drama"),
  runtime = c (134),
  imdb_rating = c (7.3), 
  critics_score = c (61)
)
snowden
```

```{r predict with model}
predict_01 <- predict(mv_bas, newdata = snowden, se.fit = TRUE, interval = "predict", estimator = "BMA")
#to show results in a table
predict_01_sum <- data.frame(
  "Title" = c("Snowden"), "Predicted audience score" = predict_01$Ybma, "Actual RT score" = c(70) )
predict_01_sum
```
Pretty good

* * *

## Part 6: Conclusion


